CS222 Project Proposal

### 2019-12-10 proposal/proposal.tex
some update of proposal

We will take the image recognition (classification) task as the example throughout the project.
At present, Boosting\cite{Schapire1989The} tends to be one possible solution.
However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
By contrast, thanks to the application of neural networks and more sophisticated combination methods, we will attempt to pursue a more robust and accurate model.

@@

There are further constraints and considerations of the optimal set of classifiers $D^*$.
\begin{itemize}
    \item \textbf{Number of Classifiers.} We need to choose adequate number of classifiers $|D^*|$ so that it covers all classes. But we prefer to use as less classifiers as possible to save computational consumptions.
    \item \textbf{Network Size.} The size of each classifier is limited. Large networks as classifiers improve accuracy but slow down inferences. Therefore, we will have penalty for large classifiers.
    \item \textbf{Overall Accuracy.} We know the accuracy of each classifier as a prior, but we need to derive the overall accuracy based on it. The $D^*$ should optimize the overall accuracy along with other goals.
\end{itemize}
These are factors we will consider in the later development and we are open for other suggestions.

Beside these factors, there are other implementation issues about the solution to the problem.
We have considered a given search space for small models, where the performance and functionality of each model is known as a prior.
This allows us to concentrate on the search part of the solution.
Nevertheless, we do not have such a prior in practice.
Instead, we need to determine the next small model to be explored during the search, which we could potentially formulate as a local search problem.

@@

% ensemble
A similar method that uses several weak learners to accomplish tasks is the ensemble method, which has been explored by many researchers. 
Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
However, this method actually increased the amount of computation since it trained the learned repeatedly.
Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieved arbitrarily high accuracy by combining a set of weak learners.
This method was developed by Freund \textit{et al.}\cite{Freund1995A}, who proposed an adaptive version of the boost.
Subsequent weak learners were tweaked in favor of those instances misclassified by previous classifiers. 
Friedman \textit{et al.}\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.

>>>>

We will take the image recognition (classification) task as the example throughout the project.
At present, boosting\cite{Schapire1989The} tends to be one possible solution.
However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
By contrast, thanks to the application of neural networks and more sophisticated combination methods, we will attempt to pursue a more robust and accurate model.

@@

There are further constraints and considerations of the optimal discriminator set $D^*$.
\begin{itemize}
    \item \textbf{Number of Classifiers.} We need to choose adequate number of classifiers $|D^*|$ so that it covers all classes. But we prefer to use as less classifiers as possible to save computational consumptions.
    \item \textbf{Network Size.} The size of each classifier is limited. Large networks as classifiers improve accuracy but slow down inferences. Therefore, we will have penalty for large classifiers.
    \item \textbf{Overall Accuracy.} We know the accuracy of each classifier as a prior, but we need to derive the overall accuracy based on it. The $D^*$ should optimize the overall accuracy along with other goals.
\end{itemize}
These are factors we will consider in the later development and we are open for other suggestions.

Beside these factors, there are other implementation issues about the solution to the problem.
We have considered a given search space for small models, where the performance and functionality of each model is known as a prior.
This allows us to concentrate on the search part of the solution.
Nevertheless, we do not have such a prior in practice.
Instead, we need to determine the next small model to be explored during the search, which we could formulate as a local search problem.

@@

% ensemble
A similar method that uses several weak learners to accomplish tasks is the ensemble method, which has been explored by many researchers. 
Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
However, this method actually increased the amount of computation since it trained the learned repeatedly.
Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieved arbitrarily high accuracy by combining a set of weak learners.
This method was developed by Freund \textit{et al.}\cite{Freund1995A}, who proposed an adaptive version of the boost.
Subsequent weak learners were tweaked in favor of those instances misclassified by previous classifiers. 
Friedman \textit{et al.}\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.
We will consider to include their ideas to ensemble models in our discriminator set.
